---
title: "Using the \"forecastHybrid\" package"
author: "David Shaub"
date: "`r Sys.Date()`"
output: 
  html_document: 
    keep_md: yes
    toc: yes
vignette: >
  %\VignetteIndexEntry{Using the "forecastHybrid" package}
  \usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
---

The "forecastHybrid" package provides functions to build composite models using multiple individual component models from the "forecast" package. These ```hybridModel``` objects can then be manipulated with many of the familiar functions from the "forecast"  and "stats" packages including ```forecast()```, ```plot()```, ```accuracy()```, ```residuals()```, and ```fitted()```.

# Installation

The stable release of the package is hosted on [CRAN](https://cran.r-project.org/package=forecastHybrid/index.html) and can be installed as usual.
```{r cran_install, eval = FALSE}
install.packages("forecastHybrid")
```

The latest development version can be installed using the "devtools"" package.
```{r github_install, eval = FALSE}
devtools::install_github("ellisp/forecastHybrid/pkg")
```

Version updates to CRAN will be published frequently after new features are implemented, so the development version is not recommended unless you plan to modify the code.

# Basic usage
First load the package.
```{r load_library, message = FALSE}
library(forecastHybrid)
```

## Quick start
If you don't have time to read the whole guide and want to get started immediatly with sane default settings to forecast the ```AirPassengers``` timeseries, run the following:
```{r quickstart}
quickModel <- hybridModel(AirPassengers)
forecast(quickModel)
plot(forecast(quickModel))
```

## Fitting a model
The workhorse function of the package is ```hybridModel()```, a function that combines several component models from the "forecast" package. At a minimum, the user must supply a ```ts``` or ```numeric``` vector for ```y```. In this case, the ensemble will include all of the component models: ```auto.arima()```, ```ets()```, ```nnetar()```, ```stlm()```, and ```tbats()```. To instead use only a subset of these models, pass a character string to the ```models``` argument with the first letter of each model to include. For example, to build an ensemble model on the ```gas``` dataset with ```auto.arima()```, ```ets()```, and ```tbats()``` components, run

```{r basic_model}

# Build a hybrid forecast on the gas dataset using auto.arima, ets, and tbats models.
# Each model is given equal weight
hm1 <- hybridModel(y = gas, models = "aet", weights = "equal")
```

The individual component models are stored inside the ```hybridModel``` objects and can viewed in their respective slots, and all the regular methods from the "forecast" package could be applied to these individual component models.
```{r individualModels}
# View the individual models
hm1$auto.arima

# See forecasts from the auto.arima model
plot(forecast(hm1$auto.arima))

```


### Model diagnostics
The ```hybridModel()``` function produces an S3 object of class ```forecastHybrid```.
```{r object_class}
class(hm1)
is.hybridModel(hm1)
```
The ```print()``` and ```summary()``` methods print information about the ensemble model including the weights assigned to each individual component model.
```{r printSummary}
print(hm1)
summary(hm1)
```

Two types of plots can be created for the created ensemble model: either a plot showing the actual and fitted value of each component model on the data or individual plots of the component models as created by their regular S3 ```plot()``` methods. Note that a ```plot()``` method does not exist in the "forecast" package for objects generated with ```stlm()```, so this component model will be ignored when ```type = "models"```, but the other component models will be plotted regardless.
```{r plots}
plot(hm1, type = "fit")
plot(hm1, type = "models")

```

By default each component model is given equal weight in the final ensemble. Empirically this has been shown to give good performance in ensembles [see @Armstrong2001], but alternative combination methods are available: the inverse root mean square error (```RMSE```), inverse mean absolute error (```MAE```), and inverse mean absolute scaled error (```MASE```). To apply one of these weighting schemes of the component models, pass this value to the ```errorMethod``` argument and pass either ```"insample.errors"``` or ```"cv.errors"``` (currently unimplemented) to the ```weights``` argument.
```{r errorMethod}
hm2 <- hybridModel(wineind, weights = "insample.errors", errorMethod = "MASE")
hm2
```
After the model is fit, these weights are stored in the ```weights``` attribute of the model. The user can view and manipulated these weights after the fit is complete. Note that the ```hybridModel()``` function automatically scales weights to sum to one, so a user should similar scale the weights to ensure the forecasts remain unbiased. Furthermore, the vector that replaces ```weights``` must retain names specifying the component model it corresponds to since weights are not assigned by position but rather by component name. Similarly, indiviudal components may also be replaced
```{r viewWeights}
hm2$weights
newWeights <- c(0.1, 0.2, 0.3, 0.1, 0.3)
names(newWeights) <- c("auto.arima", "ets", "nnetar", "stlm", "tbats")
hm2$weights <- newWeights
hm2
hm2$weights[1] <- 0.2
hm2$weights[2] <- 0.1
hm2
```

This ```hybridModel``` S3 object can be manipulated with the same familiar interface from the "forecast" package, including S3 generic functions such as ```accuracy```, ```forecast```, ```fitted```, and ```residuals```.
```{r generics}
# View the first 10 fitted values and residuals
head(fitted(hm1))
head(residuals(hm1))
```

In-sample errors and various accuracy measure can be extracted with the ```accuracy``` method. The "forecastHybrid" package creates an S3 generic from the ```accuracy``` method in the "forecast" package, so ```accuracy``` will continue to function as normal with objects from the "forecast" package, but now special functionality is created for ```hybridModel``` objects. To view the in-sample accuracy for the entire ensemble, a simple call can be made.
```{r accuracy_ensemble}
accuracy(hm1)
```
Rather that retrieving the ensemble's accuracy, the individual component models' accuracies can be easily viewed by using the ```individual = TRUE``` argument.
```{r accuracy_individual}
accuracy(hm1, individual = TRUE)
```

## Forecasting
Now's let's forecast future values. The ```forecast()``` function produce an S3 class ```forecast``` object for the next 48 periods from the ensemble model. 
```{r basic_forecast}
hForecast <- forecast(hm1, h = 48)
```

Now plot the forecast for the next 48 periods. The prediction intervals are preserved from the individual component models and currently use the most extreme value from an individual model, producing a conservative estimate for the ensemble's performance.
```{r plot_forecast}
plot(hForecast)
```

# Advanced usage
The package aims to make fitting ensembles easy and quick, but it still allows advanced tuning of all the parameters available in the "forecast" package. This is possible through usage of the ```a.args```, ```e.args```, ```n.args```, ```s.args```, and ```t.args``` lists. These optional list arguments may be applied to one, none, all, or any combination of the included individual component models. Consult the documentation in the "forecast" package for acceptable arguments to pass in the ```auto.arima```, ```ets```, ```nnetar```, ```stlm```, and ```tbats``` functions.
```{r advanced_fit}
hm2 <- hybridModel(y = gas, models = "aenst",
                   a.args = list(max.p = 12, max.q = 12, approximation = FALSE),
                   n.args = list(repeats = 50),
                   s.args = list(robust = TRUE),
                   t.args = list(use.arma.errors = FALSE))
```

Since the ```lambda``` argument is shared between all the models in the "forecast" framework, it is included as a special paramemeter that can be used to set the Box-Cox transform in all models instead of settings this individually. For example,

```{r lambda}
hm3 <- hybridModel(y = wineind, models = "ae", lambda = 0.15)
hm3$auto.arima$lambda
hm3$ets$lambda
```

Users can still apply the ```lambda``` argument through the tuning lists, but in this case the list-supplied argument overwrites the default used across all models. Compare the following two results.
```{r advancedLambda}
hm4 <- hybridModel(y = wineind, models = "aens", lambda = 0.2,
                   a.args = list(lambda = 0.5),
                   n.args = list(lambda = 0.6))
hm4$auto.arima$lambda
hm4$ets$lambda
hm4$nnetar$lambda
hm4$stlm$lambda

```

Covariates can also be supplied to ```auto.arima``` and ```nnetar``` models as is done in the "forecast" package. To do this, utilize the ```a.args``` and ```n.args``` lists. Unlike the usage in the "forecast" package, the ```xreg``` argument should be passed as a dataframe, not a matrix. If a ```xreg``` is used in training, it must also be supplied to the ```forecast()``` fucntion in the ```xreg``` argument. Note that if the number of rows in the ```xreg``` to be used for the forecast does not match the supplied ```h``` forecast horizon, the function will overwrite ```h``` with the number of rows in ```xreg``` and issue a warning.
```{r xreg}
# Use the beaver1 dataset with the variable "activ" as a covariate and "temp" as the timeseries
# Divice this into a train and test set
trainSet <- beaver1[1:100, ]
testSet <- beaver1[-(1:100), ]
trainXreg <- data.frame(trainSet$activ)
testXreg <- data.frame(testSet$activ)

# Create the model
beaverhm <- hybridModel(trainSet$temp,
                        models = "aent",
                        a.args = list(xreg = trainXreg),
                        n.args = list(xreg = trainXreg))
# Forecast future values
beaverfc <- forecast(beaverhm, xreg = testXreg)

# View the accuracy of the model
accuracy(beaverfc, testSet$temp)
```
